Spoken Corpus of Karel Mako\v{n}

### 2018-04-13 2018-clarin-pisa/makon-data.tex
conclusion clarin2018

>>>>

\section{Conclusion}

With its length of over 1000 hours spoken by a single speaker over three
decades, the corpus of Karel Mako\v{n} is a unique piece in the Lindat/Clarin
repository. The consistent domain of Christian mystic is another of its
distinguishing features. A basis for detailed topical analysis is presented
exploiting the existing transcription and the author's books.
